Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy

### 2017-03-08 paper/letter.tex
other typos

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report do not include any dust model.
Here we use an analytical solution that captures the most important
effects of rotation onto the \lya\ line as explained by
\citet{GaravitoCamargo2014} and allows us a full parameter space
exploaration.

@@

A new observational test is needed to clarify the kinematical nature of
\tol. 
We suggest that integral field unit measurements 
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map.
We note that archival Chandra X-ray archival
data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol\. This lack of observations also puts an upper
limit on the intensity of recent black hole activity.

Another observational test includes the measurement of the
\lya\ ionizing continuum escape fraction.
In the rotational model this fraction should be zero, while
the multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle \citep{2014MNRAS.444.1095G}. 
recent

@@

\section*{Acknowledgments}
We thanks J. M. Mas-Hesse for providing us with \tol's observational
\lya\ data in electronic format. This data was used to prepare Figure
1.

>>>>

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report do not include any dust model.
Here we use an analytical solution that captures the most important
effects of rotation onto the \lya\ line as explained by
\citet{GaravitoCamargo2014} and allows us a full parameter space
exploration.

@@

A new observational test is needed to clarify the kinematical nature of
\tol. 
We suggest that integral field unit measurements 
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map.
We note that archival Chandra X-ray archival
data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol. This lack of observations also puts an upper
limit on the intensity of recent black hole activity.

Another observational test includes the measurement of the
\lya\ ionizing continuum escape fraction.
In the rotational model this fraction should be zero, while
the multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle \citep{2014MNRAS.444.1095G}.

@@

\section*{Acknowledgments}
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya\ data in electronic format. This data was used to prepare Figure
1.
